Universal Anonymous Signatures

### 2022-05-13 prism-backend/research/gsac/preliminaries.tex
Quick full pass (excl. appendices).

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, or commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
produces the public parameters for the scheme.
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
key pair. $\\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
  \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
and a signer, who owns signing key \SBCMsk; both also receive common input a
block of messages \smsg. The output of the protocol is a signature over
$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
\sig,\overline{\smsg},\smsg)$ verifies a signature \SBCMsig over message set
$\overline{\smsg} \cup \smsg$. In addition, the
produced signatures must be compatible with (efficient) NIZK proofs of knowledge
of a signature, and of (arbitrary) claims over the signed (committed) messages.
An \SBCM scheme must provide one-more-forgery type of security.

@@

We use common notation habits. $y \gets A(x)$ means that algorithm $A$, on input
$x$, produces output $y$. When $A$ is a probabilistic process, and we want to
make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B \gets
\langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$, running an
interactive protocol, where $A$ receives $x_A$ as input and produces $y_A$ as
output, and $B$ receives $x_B$ and produces $y_B$.
%
Our generic constructions
rely on the previously defined building blocks, which share common (but different
tokens): e.g., we will resort to several NIZK proofs instances. To distinguish
them, we may use subscripts or superscripts: e.g., $\NIZKRel_A$ denotes the
NP relation used within some algorithm $A$, $\NIZKSetupRel$ means that
the setup algorithm of an underlying NIZK system is performed associated to
relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
and $\Eparm$ are the public parameters for an encryption scheme. Variables
written in bold font denote sets, e.g., while we use \ipk to denote a single
issuer public key, \sipk denotes a set of issuer's public keys.
%
We also assume the existence of a well defined attribute space over which
issuers in our schemes can issue credentials on. We denote this set with
\AttrSpace.

>>>>

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing blocks of messages, or commitments
to blocks of messages, and which are furthermore compatible with (efficient)
proof systems over the produced signature and signed (commitments to) messages.
For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
produces the public parameters for the scheme. %
$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
key pair. $\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
  \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
and a signer, who owns signing key \sk; both also receive common input a
block of messages \smsg. The output of the protocol is a signature over
$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message set
$\overline{\smsg} \cup \smsg$. In addition, the
produced signatures must be compatible with (efficient) NIZK proofs of knowledge
of a signature, and of (arbitrary) claims over the signed (committed) messages.
An \SBCM scheme must provide one-more-forgery type of security.

@@

We follow common notation habits. $y \gets A(x)$ means that algorithm $A$, on
input $x$, produces output $y$. When $A$ is a probabilistic process, and we want
to make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B
\gets \langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$, running an
interactive protocol, where $A$ receives $x_A$ as input and produces $y_A$ as
output, and $B$ receives $x_B$ and produces $y_B$.
%
Our generic constructions
rely on the previously defined building blocks, which share common (but different
tokens): e.g., we will resort to several NIZK proofs instances. To distinguish
them, we may use subscripts or superscripts: e.g., $\NIZKRel_A$ denotes the
NP relation used within some algorithm $A$, $\NIZKSetupRel$ means that
the setup algorithm of an underlying NIZK system is performed associated to
relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
and $\Eparm$ are the public parameters for an encryption scheme. Variables
written in bold font denote sets, e.g., while we use \ipk to denote a single
issuer public key, \sipk denotes a set of issuer's public keys. To refer to
a specific element of a set, we use subindexes, e.g., $\sipk_i$ is the $i$-th
\ipk within \sipk.
%
We also assume the existence of a well defined attribute space over which
issuers in our schemes can issue credentials on. We denote this set with
\AttrSpace.

### 2022-05-13 prism-backend/research/gsac/sec-gsac.tex
Quick full pass (excl. appendices).

\begin{itemize}
\item Enables a natural way to incorporate accountability within 
  privacy-preserving identities. Furthermore, it does so in a formal way,
  via the traceability notion and, crucially, the non-frameability one,
  (which is not present in anonymous credentials).
\item Provides meaning to the conventional \Open functionality of group
  signatures, which traditionally has only required that an abstract concept of
  ``identity'' be returned. Concretely, assuming honest issuance (which is
  already a requirement in anonymous credentials; and in group signatures for
  traceability), we can make specific claims about the attributes associated to
  de-anonymized signers. Otherwise, without integrating attributes within the
  issued credentials, the value returned by \Open serves barely for blacklisting
  or similar functionalities -- but otherwise gives no information straight away
  about the signer's identity, forcing implementors to rely to non-cryptographic
  means to retrieve such information.
\end{itemize}

\paragraph{Intuition for our design and construction.} %
Functionally, we combine both worlds. Namely, a user can get as many credentials
as s/he wants -- although all are tied to the same user key --, and signatures
(or credential presentations) of the same credential must be unlinkable. In this
simplified first step, we restrict to selective attribute disclosure, meaning
that signatures produced by a credential reveal only a subset of the attributes
in that credential. Given such a signature, there is a trusted opener who can
de-anonymize its signer, producing back its public key, as well as a proof of
correct opening.

With respect to the model, privacy-wise this direct combination requires that
any two signatures (credential presentations) reveal nothing about the
credential used to produce them, beyond the revealed attributes. For this first
step, security-wise we stick to the conventional separation of
unforgeability-related properties in group signatures. That is, traceability
requires that, in the presence of an honest issuer, all valid signatures must
originate from a credential issued by the issuer; and, from the AC domain, we
import the requirement that no user can claim having attributes that have not
been issued to a single credential. As in group signatures, if the issuer is
corrupt, all we can hope for is that honest users do not get undeserved blame;
but, other than that, the adversary can obviously obtain credentials with
arbitrary attributes. Still, note that this is a clear gain with respect to
conventional anonymous credential systems, which offer no security against a
malicious issuer.
%
Finally, in this first step, we restrict ourselves to signatures/presentations
involving only one credential, to a system with only one issuer and opener  and,
as stated, to selective attribute disclosure.

>>>>

\begin{itemize}
\item Enables a natural way to incorporate accountability within 
  privacy-preserving identities. Furthermore, it does so in a formal way,
  via the traceability notion and, crucially, the non-frameability one
  (which is not present in anonymous credentials).
\item Provides meaning to the conventional \Open functionality of group
  signatures, which traditionally has only required that an abstract concept of
  ``identity'' be returned. Concretely, assuming honest issuance (which is
  already a requirement in anonymous credentials; and in group signatures for
  traceability), we can make specific claims about the attributes associated to
  de-anonymized signers. Otherwise, without integrating attributes within the
  issued credentials, the value returned by \Open serves barely for blacklisting
  or similar functionalities -- but otherwise gives no information straight away
  about the signer's identity, forcing implementors to rely to non-cryptographic
  means to retrieve such information.
\end{itemize}

\paragraph{Intuition for our design and construction.} %
Functionally, we combine both worlds. Namely, a user can get as many credentials
as s/he wants -- although all are bound to the same user key --, and signatures
(or credential presentations) of the same credential must be unlinkable. In this
simplified first step, we restrict to selective attribute disclosure, meaning
that signatures produced by a credential reveal only a subset of the attributes
in that credential. Given such a signature, there is a trusted opener who can
de-anonymize its signer, producing back its public key, as well as a proof of
correct opening.

With respect to the model, privacy-wise this direct combination requires that
any two signatures (credential presentations) reveal nothing about the
credential used to produce them, beyond the revealed attributes.
Security-wise we stick to the conventional separation of
unforgeability-related properties in group signatures. That is, traceability
requires that, in the presence of an honest issuer, all valid signatures must
originate from a credential issued by the issuer; and, from the AC domain, we
import the requirement that no user can claim having attributes that have not
been issued to a single credential. As in group signatures, if the issuer is
corrupt, all we can hope for is that honest users do not get undeserved blame;
but, other than that, the adversary can obviously obtain credentials with
arbitrary attributes. Still, note that this is a clear gain with respect to
conventional anonymous credential systems, which offer no security against a
malicious issuer.
%
Finally, in this first step, we restrict ourselves to signatures/presentations
involving only one credential, to a system with only one issuer and opener  and,
as stated, to selective attribute disclosure.

### 2022-05-13 prism-backend/research/gsac/sec-uas.tex
Quick full pass (excl. appendices).

Furthermore, to make the concept more flexible, we no longer restrict to the
case of one issuer and one opener. Instead, \UAS supports multiple issuers (as
in generalized variants of anonymous credentials), as well as multiple openers,
each one with a predefined open function. Thus, it supports use cases like
having a user produce a signature with credentials obtained from issuers A and
B, which can be inspected by opener C; but later use the same credentials
from issuers A and B, to produce a signature that can be inspected by opener D.
A consequence of this is that the concept of ``group'', which was very present
in \GSAC, is now blurred in \UAS, and we get closer to the context of anonymous
credentials -- while still offering the accountability we inherit from \GSAC
via \Open and \Judge.

>>>>

Furthermore, to make the concept more flexible, we no longer restrict to the
case of one issuer and one opener. Instead, \UAS supports multiple issuers (as
in generalized variants of anonymous credentials), as well as multiple openers,
each one with a predefined open function. 
A consequence of this is that the concept of ``group'', which was very present
in \GSAC, is now blurred in \UAS, and we get closer to the context of anonymous
credentials -- while still offering the accountability we inherit from \GSAC
via \Open and \Judge.
%
Although this may seem an innocent change, it brings much flexibility in
practice.

### 2022-05-13 prism-backend/research/gsac/security-uas.tex
Quick full pass (excl. appendices).

\begin{theorem}[Correctness of \CUASGen]
  \label{thm:correctness-uas}
  If the underlying schemes for commitments, encryption and \SBCM, are correct,
  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
  defined in \defref{def:correctness-uas}.
\end{theorem}

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}
  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is simulation extractable
  and sound, then our \CUASGen construction satisfies issuance unforgeability as
  defined in \defref{def:issue-forge-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:issue-forge-uas}; Issue unforgeability of \CUASGen]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. As per the definition of
  \NIZK in \appref{sapp:nizk}, both games are indistinguishable.

>>>>

\begin{theorem}[Correctness of \CUASGen]
  \label{thm:correctness-uas}
  If the underlying schemes for commitments, public-key encryption and \SBCM,
  are correct,
  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
  defined in \defref{def:correctness-uas}.
\end{theorem}

@@

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}
  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
  simulation extractable and sound, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:issue-forge-uas}; Issue unforgeability of \CUASGen]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.

### 2022-05-13 prism-backend/research/gsac/transformations-uas.tex
Quick full pass (excl. appendices).

In order to justify \UAS's universality, in this section we describe how does
\UAS schemes relate with other similar systems. \jdv{The relationships seem
  quite straightforward; thus, we only informally sketch how one could build
  other schemes (or something very similar to them) from \UAS, and leave the
  formal analysis for futher work.}
%
As a first (informal) observation, we note that the same transformation to
interactive presentations as described in \GSAC applies here.

@@

\subsection{\UAS with Multiple Openers}
We briefly mention that we have defined \UAS signatures as being ``openable'' by
only one opener. However, since there is no tight relation between issuer and
opener (as in conventional group signatures), note that it is trivial to extend
to the case with multiple openers per signature. In that case, the
$\NIZKRel_{\Sign}$ relation should be extended to include proofs of correct
encryption of the \yinsp values produced by each chosen opener.
Similarly, the sign unforgeability and non-frameability definitions should be
extended to check correctness of the corresponding extra open values.

@@

In \cite{khk+19}, one of the first group signature schemes with a certain
flexibility in the open-related functionality was introduced. Briefly, a group
signature scheme with message dependent opening works as a conventional group
signature scheme, with the addition that it is only possible to open signatures
over specific messages (e.g., text with offensive language). For this, the
authors introduce an extra authority, the admitter, who creates a
``message-specific token'' for each message that they deem unacceptable.
These message-specific tokens are later needed by the opener, in order to open
signatures over unacceptable messages.

@@

In a nutshell, ring signatures \cite{rst06} are like group signatures where
rather than having an issuer accepting users into a group, any user can create
an ad hoc group composed by himself, and any arbitrary set of other users that
have advertised their public keys in some publicly accessible way. Also, in
ring signatures no de-anonymization is possible\footnote{At least, in vanilla
  ring signatures. Some variants allow some sort of linkability; for instance
  \cite{lww04}}, although the most distinguishing property is probably the lack
of issuer, which has led some relevant systems like Monero%
\footnote{\url{https://www.getmonero.org/resources/moneropedia/ringsignatures.html}.
  Last access on May 8th, 2022.} to opt for ring signatures rather than, e.g.,
group signatures.

To reach (vanilla) ring signatures from \UAS, we have to slightly alter our
generic construction. This is due to the fact that the NP relation
$\NIZKRel^{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
issuers' public keys. This is a problem as, intuitively, the signer in a ring
signature is a sort of issuer for the ad hoc group. To hide the issuer, we
replace the NP relation in \secref{ssec:generic-construction-uas} with
$\NIZKRel^{\Sign-prv} \coloneqq \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r,
\sipk_{\scred}),(\msg,\feval,\yeval,\Ec,\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \feval(\usk,\scred,\msg) \land \yinsp = \finsp(\yeval,\usk,\scred,\msg)
\land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,\usk,
\attrs_{\cred}) = 1) \rbrace$. That is, the public keys of the issuers are now
part of the witness in the NP relation, which means that they will not
be revealed in the proofs.
%
Besides $\NIZKRel^{\Sign-prv}$, let $ring$ be an ad hoc set containing the
public keys of the users that the signer wants to include in its ad hoc group.
We define $\fissue^{ring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
\subseteq ring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
\pcreturn 0 \rbrace$. That is, if we let the attributes in a credential be
public keys, this function means that a credential will be issued if all the
public keys specified as attributes to be included in the credential are part of
the union of the ad hoc ring and the public key of the signer. We also define
$\feval^{\attrs}(\usk,\cred,\msg) \coloneqq \lbrace \pcif \CCommit(\usk;0) \in
\attrs: \pcreturn \attrs(\cred); \pcelse \pcreturn \bot \rbrace$, where
$\attrs(\cred)$ is the function that returns all the attributes encoded in a
credential. That is, if the public key of the signer is included in the ring,
return all the attributes in the credential (i.e., all the public keys in the
ring); otherwise, abort. Finally, let $\finsp^0(\yeval,\usk,\cred,\msg) = 0$.

Then, an \UAS scheme with $\NIZKRel^{\Sign-prv}$ as NP relation for
$\NIZK^{\Sign}$, and $\fissue^{ring}$, $\feval^{\attrs}$, and $\finsp^0$ is
intuitively a ring signature scheme. To see this, observe that any user can
act as an issuer. Thus, the owner of \usk can issue to himself a credential
for any arbitrary ring it desires. While the $\NIZKRel^{\Issue}$ reveals the
issuer's public key, note that this is irrelevant, as the issuer is the user
himself. Then, the newly defined $\NIZKRel^{\Sign-prv}$ does exactly the same
as in our original \UAS scheme, but without revealing the issuer's public key.
$\feval^{\attrs}$ reveals all the attributes in the credential, which are
the public keys of the ring, including the signer's public key. This is actually
what ring signatures do: the signer, who is the owner of the private key
associated to one of the public keys in the ring, advertises which are the
public keys in the ring, and proves knowledge of one of them. If the NIZK
proof verifies, this means that the signer is indeed the owner of such a private
key. Finally, since $\finsp^0$ returns always $0$, then no de-anonymization is
possible.

@@

\commentwho{Jesus}{How to cite the Crypto22 paper?}

@@

With this alternative definition, we can achieve a generalisation of MPS
basically by, insted of returning the plaintext \yeval value, returning an
encryption of it under the opener's public key; additionally proving 
that the value used to compute the output of \finsp is the plaintext \yeval
value. In more detail, given any \feval function, we first define an
encrypted variant $\feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
\gets \feval(\usk,\scred,\msg); \yeval' \gets \EEnc(\opk,\yeval); \pcreturn
\yeval' \rbrace$.
%
Naturally, the $\NIZKRel_{\Sign}$ has to be correspondigly extended, as
$\NIZKRel_{\Sign}^{enc} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,
\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \yinsp = \finsp(\feval(\usk,
\scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$.

@@

Building delegatable credentials is also straightforward, thanks to the \fissue
function. For instance, take the simplification of level-based delegation, where
the owner of a credential of level $n$ can only issue credentials of level
$n+1$. Without loss of generality, assume that the credential level is encoded
in the first attribute of the credential, which we denote with $a_1$. In this
context, any owner of a credential of level $n$ can define an issuance function
$\fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1; \pcelse \pcreturn 0
\rbrace$.

>>>>

In order to justify \UAS's universality, in this section we describe how do
\UAS schemes relate with other similar systems. \jdv{The relationships seem
  quite straightforward; thus, we only informally sketch how one could build
  other schemes (or something very similar to them) from \UAS, and leave the
  formal analysis for futher work.}
%
As a first (informal) observation, we note that the same transformation to
interactive presentations as described in \GSAC applies here.

@@

\subsection{\UAS with Multiple Openers}
We briefly mention that we have defined \UAS signatures as being ``openable'' by
only one opener. However, since there is no tight relation between issuer and
opener (as opposed to conventional group signatures), it is trivial to
extend to the case with multiple openers per signature. In that case, the
$\NIZKRel_{\Sign}$ relation should be extended to include proofs of correct
encryption of the \yinsp values produced by each chosen opener.
Similarly, the sign unforgeability and non-frameability definitions should be
extended to check correctness of the corresponding extra open values.

@@

In \cite{khk+19}, one of the first group signature schemes with a certain
flexibility in the open-related functionality was introduced. Briefly, a group
signature scheme with message dependent opening works as a conventional group
signature scheme, with the addition that it is only possible to open signatures
over specific messages (e.g., text with offensive language). For this, the
authors introduce an extra authority, the admitter, who creates a
``message-specific token'' for each message that is deemed unacceptable.
These message-specific tokens are later needed by the opener, in order to open
signatures over unacceptable messages.

@@

In a nutshell, ring signatures \cite{rst06} are like group signatures where
rather than having an issuer accepting users into a group, any user can create
an ad hoc group composed by himself, and any arbitrary set of other users that
have advertised their public keys in some publicly accessible way. Also, in
ring signatures no de-anonymization is possible\footnote{At least, in vanilla
  ring signatures. Some variants allow some sort of linkability; for instance
  \cite{lww04}.}, although the most distinguishing property is probably the lack
of issuer, which has led some relevant systems like Monero%
\footnote{\url{https://www.getmonero.org/resources/moneropedia/ringsignatures.html}.
  Last access on May 8th, 2022.} to opt for ring signatures rather than, e.g.,
group signatures.

To reach (vanilla) ring signatures from \UAS, we have to slightly alter our
generic construction. This is due to the fact that the NP relation
$\NIZKRel_{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
issuers' public keys. This is a problem as, intuitively, the signer in a ring
signature is a sort of issuer for the ad hoc group. To hide the issuer, we
replace the NP relation in \secref{ssec:generic-construction-uas} with
$\NIZKRel^{\Sign-prv} \coloneqq \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r,
\sipk_{\scred}),(\msg,\feval,\yeval,\Ec,\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \feval(\usk,\scred,\msg) \land \yinsp = \finsp(\yeval,\usk,\scred,\msg)
\land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,\usk,
\attrs_{\cred}) = 1) \rbrace$. That is, the public keys of the issuers are now
part of the witness in the NP relation, which means that they will not
be revealed in the proofs.
%
Besides $\NIZKRel^{\Sign-prv}$, let \sring be an ad hoc set containing the
public keys of the users that the signer wants to include in its ad hoc group.
We define $\fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
\subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
\pcreturn 0 \rbrace$. That is, if we let the attributes in a credential be
public keys, this function means that a credential will be issued if all the
public keys specified as attributes to be included in the credential are part of
the union of the ad hoc ring and the public key of the signer. We also define
$\feval^{\attrs}(\usk,\cred,\msg) \coloneqq \lbrace \pcif \CCommit(\usk;0) \in
\attrs: \pcreturn \attrs(\cred); \pcelse \pcreturn \bot \rbrace$, where
$\attrs(\cred)$ is the function that returns all the attributes encoded in a
credential. That is, if the public key of the signer is included in the ring,
return all the attributes in the credential (i.e., all the public keys in the
ring); otherwise, abort. Finally, let $\finsp^0(\yeval,\usk,\cred,\msg) = 0$.

Then, an \UAS scheme with $\NIZKRel^{\Sign-prv}$ as NP relation for
$\NIZK^{\Sign}$, and $\fissue^{ring}$, $\feval^{\attrs}$, and $\finsp^0$ is
intuitively a ring signature scheme. To see this, observe that any user can
act as an issuer. Thus, the owner of \usk can issue to himself a credential
for any arbitrary ring it desires. While the $\NIZKRel^{\Issue}$ reveals the
issuer's public key, note that this is irrelevant, as the issuer is the user
himself. Then, the newly defined $\NIZKRel^{\Sign-prv}$ does exactly the same
as in our original \UAS scheme, but without revealing the issuer's public key.
$\feval^{\attrs}$ reveals all the attributes in the credential, which are
the public keys of the ring, including the signer's public key. This is actually
what ring signatures do: the signer, who is the owner of the private key
associated to one of the public keys in the ring, advertises which are the
public keys in the ring, and proves knowledge of one of them. If the NIZK
proof verifies, this means that the signer is indeed the owner of such a private
key. Finally, since $\finsp^0$ returns always $0$, then no de-anonymization is
possible.
%
Interestingly, this construction based on \UAS allows adding extra attributes
(beyond the public keys in the ring) to the produced signatures, which may be
useful for real world use cases.

@@

@@

With this alternative definition, we can achieve a generalisation of MPS
basically by, insted of returning the plaintext \yeval value, returning an
encryption of it under the opener's public key; additionally proving 
that the value used to compute the output of \finsp is the plaintext \yeval
value. In more detail, given any \feval function, we first define an
encrypted variant $\feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
\gets \feval(\usk,\scred,\msg); \yeval' \gets \EEnc(\opk,\yeval); \pcreturn
\yeval' \rbrace$.
%
Naturally, the $\NIZKRel_{\Sign}$ has to be correspondigly extended, as
$\NIZKRel_{\Sign}^{enc} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,
\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \yinsp = \finsp(\feval(\usk,
\scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$. This would
also seem to require that the used public-key encryption scheme is IND-CCA.

@@

Building delegatable credentials is also straightforward, thanks to the \fissue
function. For instance, take the simplification of level-based delegation, where
the owner of a credential of level $n$ can only issue credentials of level
$n+1$. Without loss of generality, assume that the credential level is encoded
in the first attribute of the credential (after the \usk), which we denote with
$a_1$. In this context, any owner of a credential of level $n$ can define an
issuance function $\fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
\pcelse \pcreturn 0 \rbrace$.
